The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
Comments

%Gap in Literature
Studies that explore the intent behind API modifications exist \cite{hou2011exploring}. There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the types of software evolution and software maintenance activities \cite{chapin2001types}. The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}. To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.

@@

%Purpose
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before the industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.

@@

\section{Background} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.

@@

Adaptive

@@

\smallskip \noindent
\textbf{Enhancive  }
We have found enhancive changes to be a large part of the API's evolution. Examples are...

\smallskip \noindent
\textbf{Corrective  }
Corrective changes have been a driving force for the evolution of the API...

\smallskip \noindent
\textbf{Reductive  }
Only one reductive change was found...

@@

3. Future work: Summarise what the next steps could be.
Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
       -->Suggest a similar study which looks at business factors

Random tips n trickz:
       Look up the papers from the conference (especially regarding the discussion/conclusion)
       discussion = revisiting research questions (and maybe structuring around industry/academia)
       conclusion = summary part, main final points and future work

>>>>

%Gap in Literature
Studies that explore the intent behind API modifications exist \cite{hou2011exploring}. The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}. To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.

@@

%Purpose
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.

@@

\section{Background} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study. Follow that, we will introduce the company and API examined in this study.

@@

@@

The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API. Such additions include added functionality to mechanically and digitally control the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.

Many of the changes found many deprecations which were later re-implemented as new modules. We have grouped these kinds of changes into a single type instead of two. Such examples include the deprecation and re-implementation of an event system, dynamic web page generation and configuration utilities.

The remainder of the changes were defined as general trends. These changes were not individual, but were instead larger changes that effected the whole API. Such examples include a shift towards using interfaces to access features, improved maintainability, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.

All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}. In total, thirteen unique changes were found. These changes are shown in Table \ref{table:categories}.

\smallskip \noindent
\textbf{Enhancive  }
%Define how we identified the change type
Additions or re-implementations of functionality are defined to be enhancive changes. In addition to this, we have included deprecations that have then been re-implemented to also be enhancive.
%Some Data and little explanation
53.8\% of the identified changes were given the type of enhancive. The majority of which were additions of new functionality to the API. Two examples of added functionality are the addition of camera movement module and an audio analysis module. One example of a deprecation that was re-implemented is the event system.
%Conclusion
Given that over half of the changes were identified to be enhancive, we conclude that the APIs evolution primary type of change was enhancive.

\smallskip \noindent
\textbf{Corrective  }
%Define what kinds of changes these are
Corrective changes are identified as types of change that fix broken functionality.
%Data and explanation
No corrective changes were identified between V1.0 and V2.0. There are two main reasons that we did not find any changes of this type. Firstly, the majority of changes were additions or re-implementations of functionality. This meant that most of the existing code was either removed, replaced or deprecated resulting in little to no obvious fixes. Secondly, we only had access to the public facing API and not the implementation itself. We therefore could not inspect the inner workings of the functionality that has remained between versions to determine if any corrective change took place.
%Conclusion
We therefore conclude that the evolution of the API was not driven by corrective changes.
\smallskip \noindent
\textbf{Reductive  }
%Definition
Reductive changes are defined as changes that remove or reduce functionality. This is distinctive from a deprecation as reductive types of change remove functionality completely.
%Data & Explanation
Only a single reductive type of change was identified. This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user. Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role} \cite{xing2006refactoring}, this was a surprising result. 
%Don't know if I should discuss the finding in this much depth here?
%If OK - Talk more about the business side of things, and how we couldn't identify this change ourselves
It was revealed during the interview that the functionality was removed because the case company no longer wished to support this feature, due to hardware constraints. 
%Conclusion
As this was the only reductive change found, we conclude that the evolution of the API was not primarily driven by reductive changes.

@@

3. Future work: Summarise what the next steps could be.
Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
       -->Suggest a similar study which looks at business factors
 in-depth study on each of the laws (more exhaustive) (suggested by Imed during Friday review)

Random tips n trickz:
       Look up the papers from the conference (especially regarding the discussion/conclusion)
       discussion = revisiting research questions (and maybe structuring around industry/academia)
       conclusion = summary part, main final points and future work 
       look up implications for practitioners 
       recommendations for the case company (need to put this somewhere)
